\section{Goals}
Before inspection, goals are defined in order to deeply inspect the website and to focus on the main aspect. 
\begin{itemize}
\item Read experiences of other companies and changes adopted;
\item Find the appropirate technology needed;
\item Interact with Moviri due to become a new customer;
\end{itemize}
\section{Inspection method}
We decide to adopt \textbf{MiLE heuristics} in order to inspect the website. 

\textbf{Navigation}: TODO
\begin{itemize}
\item \textbf{Interaction consistency}: do pages of the same type have the same links and interaction capability?
\item \textbf{Group navigation}: do pages of the same type have the same links and interaction capability?
\item \textbf{Structural Navigation}: is it easy to navigate among the semantic components of a Topic?
\item \textbf{Semantic Navigation}: is it easy to navigate among group members and from a group intro- ductory page to group members (and the other way around)?
\item \textbf{Landmarks}: is it easy to navigate from a Topic to a related one?
\end{itemize}

\textbf{Contents} TODO 
\begin{itemize}
\item \textbf{Information Overload}: is the information in a page too much or too little and does it fit the page layout?
\item \textbf{}
\end{itemize}

\textbf{Layout} TODO
\begin{itemize}
\item \textbf{Text Layout}: is the text readable? Is font size appropriate?
\item \textbf{Interaction Placeholder-Semiotics}: are textual or visual labels of interactive elements “expressive”? i.e., do they reflect the meaning of the interaction and its effects? Are they consistent?
\item \textbf{Interaction Placeholders-Consistency}: are textual or visual labels of interactive elements consistent in terms of wording, icon, position, etc.?
\item \textbf{Spatial Allocation}: is the on-screen allocation of contents and visual appropriate for their relevance? Are “semantically related” elements close and “semantically distant” element far away?
\item \textbf{Consistency of Page Structure}: do pages of the same type have the same lay out (same visual properties of each component and similar lay-out organization of the various elements?)
\end{itemize} 


\section{Scoring metric}




foto + click che porta in alto